Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
tdm archival edit

For the stars with AO nondetections, there is still the
possibility that a background binary could be positioned
directly behind the target star, evading detection.
The probability is small, given the $0\farcs1$ diffraction limit
of the Hale Telescope at $2$ $\mu$m, but nonzero.
We can rule out the possibility of such chance alignments with
archival imaging data.

For all targets with AO, we can confirm the planetary nature of the signal
without this extra step, but we include it for EPIC 201912552, considering
the additional follow-up this target may warrant.
We download data from the POSS I and II surveys, which imaged
EPIC 201912552 in 1955 and 1989, respectively.
This star has a proper motion of $-74 \pm 2$ mas yr$^{-1}$ in right ascension
 and $-122 \pm 4$ mas yr$^{-1}$ in declination, so it has moved by $8\farcs35$
since the POSS I data were collected.
As shown in Figure \ref{fig:archival}, we do not detect any targets at the
present-day location of EPIC 201912552 in either of the POSS surveys.

@@

For this target, we can extend our contrast curves to zero
present-day orbital separation and rule out the possibility that
these transit events are caused by a background eclipsing binary.
By combining present-day seeing-limited photometric survey data,
adaptive optics imaging, and archival photometry, the only stellar companions
we would not detect would be those that are gravitationally bound to the target
star and positioned in their orbits so that their projected separation is
smaller than the diffraction limit of the Hale Telescope.
Such an alignment would require the orbital inclination of the binary to be
nearly $90^\circ$ and the phase $\varpi + \theta \approx \pi/2$ or $3\pi/2$.
While we cannot fully rule out this possibility, such an alignment is unlikely
to occur and unable to cause enough dilution to call the planetary
nature of this signal into question.

>>>>

For the stars with AO nondetections, there is still the
possibility that a background binary could be positioned
directly behind the target star, evading detection.
The probability is small, given the $0\farcs1$ diffraction limit
of the Hale Telescope at $2$ $\mu$m, but nonzero.  
While the \texttt{vespa} calculations quantify this probability for
this to occur, we can also rule out the possibility of such
chance alignments, down to a certain contrast, with archival imaging data.

We include this extra analysis step for EPIC 201912552, considering
the additional follow-up this target may warrant.
We download data from the POSS I and II surveys, which imaged
EPIC 201912552 in 1955 and 1989, respectively.
This star has a proper motion of $-74 \pm 2$ mas yr$^{-1}$ in right ascension
 and $-122 \pm 4$ mas yr$^{-1}$ in declination, so it has moved by $8\farcs35$
since the POSS I data were collected.
As shown in Figure \ref{fig:archival}, we do not detect any targets at the
present-day location of EPIC 201912552 in either of the POSS surveys.

@@

For this target, we can extend our contrast curves to zero
present-day orbital separation and rule out the possibility that
these transit events are caused by a background eclipsing binary.
By combining present-day seeing-limited photometric survey data,
adaptive optics imaging, and archival photometry, the only stellar companions
we would not detect would be those that are gravitationally bound to the target
star and positioned in their orbits so that their projected separation is
smaller than the diffraction limit of the Hale Telescope.
Such an alignment would require the orbital inclination of the binary to be
nearly $90^\circ$ and the phase $\varpi + \theta \approx \pi/2$ or $3\pi/2$.
While we cannot fully rule out this possibility, the \texttt{vespa}
calculations confirm that its probability is negligibly small.
